Reasoning About a Machine with Local Capabilities

### 2019-02-05 toplas/preamble-illu.tex
Minor textual updates
Make various small improvements to the TOPLAS paper

\newcommand{\stdstackstart}{
  \scope
    \clip (-.1,-.1) rectangle (4.6,11.1);
    \fill[fill=white] (0,0) rectangle (4.5,11);
    \draw (0,0) -- (0,11);
    \draw (4.5,0) -- (4.5,11);
    \draw[fill=gray!50] (0,-.5) rectangle (4.5,2)
    node[pos=.5,color=black,align=center,yshift=0.1cm] {\footnotesize Higher
      stack\\\footnotesize frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
  \draw (-1.5,0) node {};
  \draw (-1.5,15) node {};
}

>>>>

\newcommand{\stdstackstart}{
  \scope
    \clip (-.1,-.1) rectangle (4.6,11.1);
    \fill[fill=white] (0,0) rectangle (4.5,11);
    \draw (0,0) -- (0,11);
    \draw (4.5,0) -- (4.5,11);
    \draw[fill=gray!50] (0,-.5) rectangle (4.5,2)
    node[pos=.5,color=black,align=center,yshift=0.1cm] {\footnotesize Lower
      stack\\\footnotesize frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
  \draw (-1.5,0) node {};
  \draw (-1.5,12) node {};
}
